Epilepsy example

### 2022-11-07 src/epil/epil.Rmd
Can create obj_fixed_theta using epil_index now (but then getting "initial value in 'vmmin' is not finite" type errors)

```{r}
xi_laplace_marginal_nu <- function(i, opt_theta, finegrid) {
  #' To fill
}
```

@@

for(theta in theta_names) {
  map_fixed_theta[[theta]] <- factor(NA)
  param[[theta]] <- opt_theta$par[[theta]]
}

@@

# obj_fixed_theta <- MakeADFun(
#   data = dat,
#   parameters = param_fixed_theta,
#   random = get_random(dat),
#   DLL = "epil_index",
#   silent = TRUE,
#   map = map_fixed_theta
# )
#   
# quad <- aghq::aghq(
#   ff = obj_fixed_theta,
#   k = 3,
#   startingvalue = 0,
#   control = aghq::default_control_tmb()
# )
# 
# pdf_and_cdf <- aghq::compute_pdf_and_cdf(quad, finegrid = finegrid)[[1]]
```

>>>>

@@

@@

obj_fixed_theta <- MakeADFun(
 data = dat,
 parameters = param_fixed_theta,
 random = get_random(dat),
 DLL = "epil_index",
 silent = TRUE,
 map = map_fixed_theta
)

# quad <- aghq::aghq(
#   ff = obj_fixed_theta,
#   k = 3,
#   startingvalue = 0,
#   control = aghq::default_control_tmb()
# )
#  
# pdf_and_cdf <- aghq::compute_pdf_and_cdf(quad, finegrid = fine_grid)[[1]]
# 
# ggplot(pdf_and_cdf, aes(x = theta, y = pdf)) +
#   geom_line() +
#   theme_minimal() +
#   labs(x = "nu[1]", y = "Posterior")
```
